Pillar 1 - Sequential Pattern Mining

### 2019-01-29 Pillar 1 - Sequential Pattern Mining.Rmd
Adds filter to subsequences to filter out not taken courses before runnning apriori

  data <- data %>%
    group_by(
      sequenceID,
      eventID
    ) %>%
    summarise(
      list_item = list(!!enquo(item))
    ) %>%
    arrange(
      sequenceID,
      eventID
    ) %>%
    ungroup

@@

## Mining Rules

### Apriori Algorithm
```{r}

@@

##rule induction:
```{r}
rules <- ruleInduction(frequent_trajectories,
                       confidence = 0, #we need to play with the parameters.
                       control    = list(verbose = TRUE))

@@

```
##calculate appropriate measures:
```{r}
n_students <- length(unique(d_sequence_transactions$`Student ID`))

>>>>

  data <- data %>%
    filter(!is.na(eventID))%>% #this is here casue we have courses that were never taken.
    group_by(
      sequenceID,
      eventID
    ) %>%
    summarise(
      list_item = list(!!enquo(item))
    ) %>%
    arrange(
      sequenceID,
      eventID
    ) %>%
    ungroup

@@

## Mining Rules
### Apriori Algorithm
```{r}

@@

##rule induction:
```{r}
rules <- ruleInduction(subsequences,
                       confidence = 0, #we need to play with the parameters.
                       control    = list(verbose = TRUE))

@@

##calculate appropriate measures:
```{r}
n_students <- length(unique(d_sequence_transactions$`Student ID`))
